\SW: II. New Gravitational Lens Candidates from the CFHTLS Discovered through Citizen Science

### 2015-05-09 doc/sw-cfhtls.tex
Up to discussion section #203

% % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % % %
\subsection{Image separation distribution}
\label{sec:results:isd}

@@

Indeed, we have found {\bf 59} new lens candidates that were not known
before. In \Fref{fig:isd}, we show the image separation distribution for
the known \rf and \af sample (green), for the \sw identified (known and
new) lens sample (blue) only and combined \cfhtls sample of \rf, \af and
the new \sw lens sample (magenta). It is interesting to note that both
the \rf$+$\af and \sw samples have very similar profiles and thus, the profile of the
combined sample has not changed significantly. This implies that previous
constraints on the image separation distribution are robust and the \af
selected sample does not suffer from significant incompleteness for
medium to large $R_{\rm E}$. This is the regime that probes density
profiles of galaxy groups to clusters.

In the figure, we also show for comparison the theoretical predictions
corresponding to three density profiles, namely, isothermal sphere (IS),
NFW \citep{Navarro1997} and Total profile which has NFW and Hernquist
profiles combined with an adiabatically contracting model for dark
matter component \citep{Gnedin2004}. These curves are taken from
\citet{More2012} which gives details of the calculation of these
predictions.  With the updated sample of lens candidates, we confirm our
previous prediction that the mass density profiles of galaxy groups is
indeed similar to the Total profile.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=1.2]{isd_cfhtls_sw.pdf}
\caption{ \label{fig:isd} Image separation distribution. Comparing theoretical
predictions (solid curves) with the \cfhtls known lens samples (green)
and the combined sample of known and \sw lens candidates (magenta). The
sample of new and the known lens candidates discovered from \sw alone is
shown in blue. The new updated profile of the isd (magenta) is
consistent with our previous measurements and strengthens our conclusion
that the average density profiles of the lenses are similar to the Total
profile.}
\end{center}
\end{figure}

>>>>

\subsection{Image separation distribution}
\label{sec:results:isd}

@@

Indeed, we have found 59 new medium and high grade
lens candidates that were not known
before. In \Fref{fig:isd}, we show the image separation distribution for
the known \rf and \af sample (green), for the \sw identified (known and
new) lens sample (blue) only and combined \cfhtls sample of \rf, \af and
the new \sw lens sample (magenta). It is interesting to note that both
the \rf$+$\af and \sw samples have very similar profiles and thus, the profile of the
combined sample has not changed significantly. This implies that previous
constraints on the image separation distribution are robust and the \af
selected sample does not suffer from significant incompleteness for
medium to large $R_{\rm E}$. This is the regime that probes density
profiles of galaxy groups to clusters.

In the figure, we also show for comparison the theoretical predictions
corresponding to three density profiles, namely, isothermal sphere (IS),
NFW \citep{Navarro1997} and a ``Total'' profile which has NFW and Hernquist
profiles combined with an adiabatically contracting model for dark
matter component \citep{Gnedin2004}. These curves are taken from
\citet{More2012}, which gives details of the calculation of these
predictions.  With the updated sample of lens candidates, we confirm our
previous prediction that the mass density profiles of galaxy groups is
indeed similar to the Total profile.

@@

\begin{figure}
\begin{center}
\includegraphics[scale=1.2]{isd_cfhtls_sw.pdf}
\caption{ \label{fig:isd} Image separation distribution (ISD). Comparing theoretical
predictions (solid curves) with the \cfhtls known lens samples (green)
and the combined sample of known and \sw lens candidates (magenta). The
sample of new and the known lens candidates discovered from \sw alone is
shown in blue. The new updated profile of the ISD (magenta) is
consistent with our previous measurements and strengthens our conclusion
that the average density profiles of the lenses are similar to the Total
profile.}
\end{center}
\end{figure}
